Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-18 documents/mixtures/mixture_models.tex
residuals no longer look bad

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.png}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.
  The residuals look bad in the logarithmic plot, but they are only
  bad very near the profile center (as expected), where the effect of
  any realistic point-spread function will average them away.}
\end{figure}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.png}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.}
\end{figure}
